---
title: "R Notebook"
output: html_notebook
---

```{r}
# required libraries

library("RStoolbox")
library("raster")
library("rgdal")
library("ggplot2")
library("SDMTools")

```



```{r}
# load tif using stack function instead raster

ortho_p3.stack <- stack("../6_qgis/output/orthomosaic_parcela3_photoscan_georreferenced.tif")
class(ortho_p3.stack)

```



```{r}
# load parcela 1
library(rgeos)
parcelas <- readOGR("../6_qgis/input/alamala.kml", "alamala")[0]
nrowdim <- dim(parcelas@data)
parcelas@data$id <- c(rep(1:nrowdim))
parcela3 <- subset(parcelas, parcelas@data$id %in% c(9,10, 11, 12))
p3.centroid.df <- as.data.frame(gCentroid(parcela3, byid = TRUE)) # extract to label parcels
class(parcela3)
plot(parcela3)

```

```{r}
parcela3.df <- fortify(parcela3) # to plot with ggplot
head(parcela3.df)
```

```{r}


# Set all pixels to NA, where bands are 0 (remove black background)
# Check if results are affected
# instead use crop and mask together (ver más adelante)

ortho_p3.stack[ortho_p3.stack[,] == 0] <- NA


# plot scene using ggRGB (from ggplot and RStoolbox)
ggRGB(ortho_p3.stack, r = 1, g = 2, b = 3, maxpixels = 2e+05, stretch="none", geom_raster = TRUE) + 
    geom_path(data = parcela3.df, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    geom_text(data = p3.centroid.df, aes(label = c("3.1", "3.2", "3.3", "3.4") ,y = y, x = x + 0.0002), colour = "white") +
    coord_equal() +
    theme_bw()
```


```{r}
ggsave("figures/parcela3.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


Extraemos las parcelas

```{r}
# crop and mask whole area

ortho_p3.stack_p3 <- crop(mask(ortho_p3.stack, parcela3),parcela3)

```


```{r}

# crop parcela 3.1

parcela31 <- subset(parcelas, parcelas@data$id %in% c(9))
ortho_p3.stack_p31 <- crop(mask(ortho_p3.stack_p3, parcela31), parcela31)
 
# crop parcela 1.2
parcela32 <- subset(parcelas, parcelas@data$id %in% c(10))

ortho_p3.stack_p32 <- crop(mask(ortho_p3.stack_p3, parcela32), parcela32)

# crop parcela 1.2
parcela33 <- subset(parcelas, parcelas@data$id %in% c(11))

ortho_p3.stack_p33 <- crop(mask(ortho_p3.stack_p3, parcela33), parcela33)


# crop parcela 1.2
parcela34 <- subset(parcelas, parcelas@data$id %in% c(12))

ortho_p3.stack_p34 <- crop(mask(ortho_p3.stack_p3, parcela34), parcela34)


```

Plot parcels

```{r}

ggRGB(ortho_p3.stack_p3, r = 1, g = 2, b = 3) + 
    geom_path(data = parcela3.df, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    theme_bw()
```


Plot parcel 3.1

```{r}
p31 <- subset(parcela3.df, id == 8)

ggRGB(ortho_p3.stack_p31, r = 1, g = 2, b = 3) + 
    geom_path(data = p31, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.1") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```
```{r}
ggsave("figures/parcela3_1.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


```{r}
ggRGB(ortho_p3.stack, r = 1, g = 2, b = 3) + 
    geom_path(data = p31, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.1") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```

```{r}
ggsave("figures/parcela3_1_ortho.pdf", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

Plot parcel 3.2

```{r}
p32 <- subset(parcela3.df, id == 9)

ggRGB(ortho_p3.stack_p32, r = 1, g = 2, b = 3) + 
    geom_path(data = p32, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.2") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```
```{r}
ggsave("figures/parcela3_2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```



```{r}
ggRGB(ortho_p3.stack, r = 1, g = 2, b = 3) + 
    geom_path(data = p32, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.2") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```


```{r}
ggsave("figures/parcela3_2_ortho.pdf", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


Plot parcel 3.3

```{r}
p33 <- subset(parcela3.df, id == 10)

ggRGB(ortho_p3.stack_p33, r = 1, g = 2, b = 3) + 
    geom_path(data = p33, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.3") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```
```{r}
ggsave("figures/parcela3_3.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```




```{r}
ggRGB(ortho_p3.stack, r = 1, g = 2, b = 3) + 
    geom_path(data = p33, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.2") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```


```{r}
ggsave("figures/parcela3_3_ortho.pdf", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


Plot parcel 3.4

```{r}
p34 <- subset(parcela3.df, id == 11)

ggRGB(ortho_p3.stack_p34, r = 1, g = 2, b = 3) + 
    geom_path(data = p34, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.4") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```
```{r}
ggsave("figures/parcela3_4.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


```{r}
ggRGB(ortho_p3.stack, r = 1, g = 2, b = 3) + 
    geom_path(data = p34, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 3.4") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```


```{r}
ggsave("figures/parcela3_4_ortho.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```



Calculate VIs

```{r}

p31.VIs <- spectralIndices(ortho_p3.stack_p31, green = 3, red=2, nir =1, indices=c("NDVI", "MSAVI2", "GNDVI"))
breaks <- seq(0, 1, by=0.01)

plot(p31.VIs)
```
Plot VI one by one


NDVI Parcela 3.1

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p31.VIs$NDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.1") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```
And save

```{r}
ggsave("figures/parcela3_1_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


MSAVI2 Parcela 3.1

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p31.VIs$MSAVI2, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.1") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```
And save

```{r}
ggsave("figures/parcela3_1_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


GNDVI Parcela 1.1

```{r}
ggR(p31.VIs$GNDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.1") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_1_GNDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


```{r}

p32.VIs <- spectralIndices(ortho_p3.stack_p32, green = 3, red=2, nir =1, indices=c("NDVI", "MSAVI2", "GNDVI"))
breaks <- seq(0, 1, by=0.01)

plot(p32.VIs)
```

NDVI Parcela 3.2

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p32.VIs$NDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.2") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_2_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

MSAVI2 Parcela 3.2

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p32.VIs$MSAVI2, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.1") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_2_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

GNDVI Parcela 3.2

```{r}
ggR(p32.VIs$GNDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.2") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_2_GNDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

```{r}

p33.VIs <- spectralIndices(ortho_p3.stack_p33, green = 3, red=2, nir =1, indices=c("NDVI", "MSAVI2", "GNDVI"))
breaks <- seq(0, 1, by=0.01)

plot(p33.VIs)
```

NDVI Parcela 3.3

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p33.VIs$NDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.3") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_3_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

MSAVI2 Parcela 3.3

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p33.VIs$MSAVI2, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.3") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_3_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

GNDVI Parcela 3.3

```{r}
ggR(p33.VIs$GNDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.3") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_3_GNDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

```{r}

p34.VIs <- spectralIndices(ortho_p3.stack_p34, green = 3, red=2, nir =1, indices=c("NDVI", "MSAVI2", "GNDVI"))
breaks <- seq(0, 1, by=0.01)

plot(p34.VIs)
```

NDVI Parcela 3.4

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p34.VIs$NDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.4") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_4_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

MSAVI2 Parcela 3.4

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p34.VIs$MSAVI2, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.4") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_4_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

GNDVI Parcela 3.4

```{r}
ggR(p34.VIs$GNDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 3.4") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

```{r}
ggsave("figures/parcela3_4_GNDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


### Exploratory data analysis of Vegetation Indices


Manual approach to explore and plot NDVI

```{r}
p31.VIs.NDVI.df <- stack(as.data.frame(p31.VIs$NDVI))
p31.VIs.NDVI.df$id <- rep("p31", length(p31.VIs.NDVI.df$ind))

p32.VIs.NDVI.df <- stack(as.data.frame(p32.VIs$NDVI))
p32.VIs.NDVI.df$id <- rep("p32", length(p32.VIs.NDVI.df$ind)) 

p33.VIs.NDVI.df <- stack(as.data.frame(p33.VIs$NDVI))
p33.VIs.NDVI.df$id <- rep("p33", length(p33.VIs.NDVI.df$ind)) 

p34.VIs.NDVI.df <- stack(as.data.frame(p34.VIs$NDVI))
p34.VIs.NDVI.df$id <- rep("p34", length(p34.VIs.NDVI.df$ind)) 

p3.VIs.NDVI <- rbind(p31.VIs.NDVI.df, p32.VIs.NDVI.df)
p3.VIs.NDVI <- rbind(p3.VIs.NDVI, p33.VIs.NDVI.df)
p3.VIs.NDVI <- rbind(p3.VIs.NDVI, p34.VIs.NDVI.df)

save(p3.VIs.NDVI, file = "data/p3_VIS_NDVI")

```



```{r}
ggplot(p3.VIs.NDVI) + 
  geom_boxplot(aes(x = id, y = values, colour=id)) +
  theme_bw() 

```

Bind indices in a whole dataframe

```{r}
library(dplyr)
library(plyr) # Tools for Splitting, Applying and Combining Data

raster_to_df <- function(x) {
  stack(as.data.frame(x))
} # convert raster to dataframe


l<- list(p31 = p31.VIs, p32 = p32.VIs, p33 = p33.VIs, p34 = p34.VIs)

l.df <- lapply(X = l, FUN = raster_to_df) # list of data frames


l.df.VIs <- ldply(l.df ,rbind) # Split list, apply function, and return results in a data frame.


```


Plot NDVI box-plot

```{r}
l.df.VIs.NDVI <-  subset(l.df.VIs, ind == "NDVI" )
ggplot(l.df.VIs.NDVI) + 
  geom_boxplot(aes(x = .id, y = values, colour=.id)) +
  facet_grid(. ~ ind) +
  theme_bw()
```

```{r}
ggsave("figures/boxplot_p31_p32_p33_p34_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

Plot MSAVI2 box-plot


```{r}
l.df.VIs.MSAVI2 <-  subset(l.df.VIs, ind == "MSAVI2" )
ggplot(l.df.VIs.MSAVI2) + 
  geom_boxplot(aes(x = .id, y = values, colour=.id)) +
  facet_grid(. ~ ind) +
  theme_bw()
```
```{r}
ggsave("figures/boxplot_p31_p32_p33_p34_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

Plot GNDVI box-plot


```{r}
l.df.VIs.GNDVI <-  subset(l.df.VIs, ind == "GNDVI" )
ggplot(l.df.VIs.GNDVI) + 
  geom_boxplot(aes(x = .id, y = values, colour=.id)) +
  facet_grid(. ~ ind) +
  theme_bw()
```

```{r}
ggsave("figures/boxplot_p31_p32_p33_p34_GNDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


Plot NDVI, GNDVI MSAVI2 histogram

```{r}

l.df.VIs.NDVI$title <- "NDVI" # fake

ggplot(l.df.VIs.NDVI, aes(x = values, colour=.id)) + 
  geom_freqpoly(aes( y=(..count..)/sum(..count..)), binwidth = 0.005) +
  facet_wrap(~title) +
  scale_y_continuous(labels=scales::percent) +
  ylab("relative frequencies") + 
  theme_bw()
```

```{r}
ggsave("figures/histo_p31_p32_p33_p34_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

```{r}

l.df.VIs.MSAVI2$title = "MSAVI2"

ggplot(l.df.VIs.MSAVI2, aes(x = values, colour=.id)) + 
  geom_freqpoly(aes( y=(..count..)/sum(..count..)), binwidth = 0.005) +
  facet_wrap(~title) +
  scale_y_continuous(labels=scales::percent) +
  ylab("relative frequencies") + 
  theme_bw()
```

```{r}
ggsave("figures/histo_p31_p32_p33_p34_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

```{r}
l.df.VIs.GNDVI$title <- "GNDVI" # fake


ggplot(l.df.VIs.GNDVI, aes(x = values, colour=.id)) + 
  geom_freqpoly(aes( y=(..count..)/sum(..count..)), binwidth = 0.005) +
  facet_wrap(~title) +
  scale_y_continuous(labels=scales::percent) +
  ylab("relative frequencies") + 
  theme_bw()
```

```{r}
ggsave("figures/histo_p31_p32_p33_p34_GNDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


# Analysis

```{r}
library('dplyr')
l.df.VIs %>% group_by(ind) %>% summarise_at("values", funs(mean, max, sd), na.rm = TRUE)

```

```{r}
library('dplyr')
l.df.VIs %>% group_by(ind, .id) %>% summarise_at("values", funs(mean, max, sd), na.rm = TRUE)
```

```{r}
saveRDS(l.df.VIs, file = "VIP3.rds")
```



```{r}
# save p41 layers
writeRaster(stack(p31.VIs), paste("p31_", names(p31.VIs), sep = ''), bylayer=TRUE, format='GTiff')
writeRaster(stack(p32.VIs), paste("p32_", names(p32.VIs), sep = ''), bylayer=TRUE, format='GTiff')
writeRaster(stack(p33.VIs), paste("p33_", names(p33.VIs), sep = ''), bylayer=TRUE, format='GTiff')
writeRaster(stack(p34.VIs), paste("p34_", names(p34.VIs), sep = ''), bylayer=TRUE, format='GTiff')

```
